Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Merge?

In order to filter high frequency effects, a SAE 600 filter was applied to the simulation results \cite{Huang}. \Cref{fig:F-D_frictionless,fig:F-D_rough} provide the force-displacement curves considering no friction and rough interaction properties respectively. In that same figure and in the upcoming ones, nomenclature is as follows:
\begin{itemize}
	\item ``A'' or ``B'' indicating the cross-section of the tube: ``A'' for the top-hat, and ``B'' for the double hat.

	\item Following that, ``R'', indicating that the rough tangential contact property was used, or ``Fl'', for the frictionless case.

	\item An ``R'' after the underline indicates that the crash box had riveting in the triggered cross section.

	\item ``Sb'' after the underline marks the presence of a stabilizing box in the model.
\end{itemize}

\begin{figure}
	\centering
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/AFl}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/BFl}
	\end{minipage}
	\caption[F-D for modeled cross sections, both top-hat and double hat, with different modeled configurations with frictionless contact.]{F-D for modeled cross sections, both top-hat (red) and double hat (blue), with different modeled configurations with frictionless contact. SEA values in brackets in $\si{\kJ/\kg}$.}
	\label{fig:F-D_frictionless}
\end{figure}

\begin{figure}
	\centering
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/BR}
	\end{minipage}
	\caption[F-D for modeled cross sections, both top-hat and double hat, with different modeled configurations with rough contact.]{F-D for modeled cross sections, both top-hat (red) and double hat (blue), with different modeled configurations with rough contact. SEA values in brackets in $\si{\kJ/\kg}$.}
	\label{fig:F-D_rough}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/peroni_qstat_fd}
	\caption[F-D obtained by \cite{Peroni2009} in quasi-static test for studied adhesive and other bonding solution.]{F-D obtained by \cite{Peroni2009} in quasi-static test for studied adhesive (blue) and other bonding solution (gray).}
	\label{fig:peroni_qstat_fd}
\end{figure}

Qualitatively, this curves are very similar to those obtained by \cite{Peroni2009}. \Cref{fig:peroni_qstat_fd} depicts a quasi-static test performed by these authors with the same section and bonding solution. Facing these similitudes, the model is considered valid.

In general, a uniform force-displacement curve would be the most desirable scenario, as it would imply maximizing the $E_\text{a}$  with the minimum $P_\text{peak}$. Thus, the best solution will be the one with the most constant-like behavior.

@@

\begin{figure}
	\centering
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a0}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a1}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a3}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a4}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a5}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a6}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a7}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a8}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a9}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a10}
	\end{minipage}

	\caption[Stable collapse mechanism achieved in the top-hat tube with stabilizing box.]{Stable collapse mechanism achieved in the top-hat tube with stabilizing box. Semi-transparent projection with adhesive in red. Total time: $\SI{15}{\ms}$; uniform spacing.}
	\label{fig:stable}
\end{figure}

@@

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/sc1.pdf}
    \caption{Baseline model.}
    \label{fig:back0}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/top_view_foam.eps}
    \caption{Specimen with the optimum SEA value.}
    \label{fig:back5}
\end{subfigure}
\end{figure}

>>>>

In order to filter high frequency effects, a SAE 600 filter was applied to the simulation results \cite{Huang}. \Cref{fig:F-D_rough} provides the obtained force-displacement curves and the results obtained in \cite{Peroni2009}. In this figure the nomenclature is as follows:
\begin{itemize}
	\item ``AR'' or ``BR'' indicating the cross-section of the tube: ``A'' for the top-hat, and ``B'' for the double hat.
	\item An ``R'' after the underline indicates that the crash box had riveting in the triggered cross section.
	\item ``Sb'' after the underline marks the presence of a stabilizing box in the model.
\end{itemize}

\begin{figure}[htpb]
	\centering
	\begin{minipage}[b]{.7\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.7\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/BR}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.7\linewidth}
		\centering
		\includegraphics[width=\linewidth]{peroni_qstat_fd}
	\end{minipage}	
	\caption[Force-displacement curves for top-hat and double hat sections with different modeled configurations.]{Force-displacement curves for top-hat and double hat sections with different modeled configurations and curves in \cite{Peroni2009}. Specific energy absorption is provided in brackets in $\si{\kJ/\kg}$.}
	\label{fig:F-D_rough}
\end{figure}

Qualitatively, this curves are very similar to those obtained by \cite{Peroni2009}. \Cref{fig:F-D_rough} depicts also a quasi-static test performed by these authors with the same section and bonding solution. Facing these similitudes, the model is considered valid. A view of the progressive collapse of the top-hat section is provided in \Cref{fig:stable}

In general, a uniform force-displacement curve would be the most desirable scenario, as it would imply maximizing the $E_\text{a}$  with the minimum $P_\text{peak}$. Thus, the best solution will be the one with the most constant response.

\begin{figure}
	\centering
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a0}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a3}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a7}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a10}
	\end{minipage}
	\caption[Stable collapse mechanism achieved in the top-hat tube with bounding box.]{Stable collapse mechanism achieved in the top-hat tube with bounding box (hidden). Semi-transparent projection with adhesive in red.}
	\label{fig:stable}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a0}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a1}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a3}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a4}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a5}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a6}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a7}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a8}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a9}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a10}
	\end{minipage}
	\caption[Stable collapse mechanism achieved in the top-hat tube with stabilizing box.]{Stable collapse mechanism achieved in the top-hat tube with stabilizing box. Semi-transparent projection with adhesive in red. Total time: $\SI{15}{\ms}$; uniform spacing.}
	\label{fig:stable}
\end{figure}

@@

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/sc1.pdf}
    \caption{Baseline model.}
    \label{fig:back0}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/topview}
    \caption{Specimen with the optimum SEA value.}
    \label{fig:back5}
\end{subfigure}
\end{figure}
